Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-05-23 demystify.tex
Updates from Overleaf

The information presented here can be useful for all students, but this guideline is primarily intended for \textbf{international students} from \textbf{smaller countries and less well-known universities} (similarly, for domestic students from universities with no PhD programs or limited research experiences). 
Students from top schools with strong research cultures and experiences might already know most of the information presented here.
My goal is thus to level the playing field by providing information that is not readily available to less privileged students. 
I also hope to encourage more students with such backgrounds to apply to CS PhD programs in the US.

While this document may not fully meet the needs of students aiming for top-10 schools, which typically have more stringent requirements (e.g., see the \href{https://da-data.blogspot.com/2015/03/reflecting-on-cs-graduate-admissions.html}{admission process} at CMU), it should be valuable for those targeting other reputable institutions, such as R1 universities in the US. It is certainly useful for students aiming for GMU!

>>>>

The guideline can be useful for all students, but it is primarily intended for \textbf{international students} from \textbf{smaller countries and less well-known universities} (similarly, for domestic students from universities with no PhD programs or limited research experiences). 
Students from top schools with strong research cultures and experiences might already know most of the information presented here.
My goal is thus to level the playing field by providing information that is not readily available to less privileged students. 
I also hope to encourage more students with such backgrounds to apply to CS PhD programs in the US.

While this document may not fully meet the needs of students aiming for top-10 schools, which typically have more stringent requirements (e.g., see the \href{https://da-data.blogspot.com/2015/03/reflecting-on-cs-graduate-admissions.html}{admission process} at CMU), it should be valuable for those targeting other R1 reputable institutions. It is certainly useful for students aiming for GMU!
